---
title: "R Notebook"
---



```{r}
library(AER)
data("GoldSilver")
```
First we check whether the data is stationary or non-stationary.
```{r}

plot(log(GoldSilver), plot.type = "single", col = c(2,4))
legend("topleft", c("Gold", "Silver"), bty = "n", col = c(2,4), lty = rep(1,2))
```

Neither of them (gold and silver prices) is stationary because:
i)	The trends are not flat, and 
ii)	the variance is not constant over time.


Next, we check for autocorrelation in the time series. 
```{r}
acf(coredata(log(GoldSilver[,"gold"])), ylim = c(-1, 1), lag.max=50)
pacf(coredata(log(GoldSilver[,"gold"])), ylim = c(-1, 1), lag.max=50)
acf(coredata(log(GoldSilver[,"silver"])), ylim = c(-1, 1), lag.max=50)
pacf(coredata(log(GoldSilver[,"silver"])), ylim = c(-1, 1), lag.max=50)

```
Based on both the plots, both gold and silver seem to exhibit random walk.

We can also perform the Dickey-Fuller and KPSS tests of stationarity for gold and silver prices. 
We perform the same test for the first-order difference of the prices

```{r}
library(tseries)
adf.test(coredata(log(GoldSilver[, "gold"])))
adf.test(diff(coredata(log(GoldSilver[, "gold"]))))
kpss.test(coredata(log(GoldSilver[, "gold"])))
kpss.test(diff(coredata(log(GoldSilver[, "gold"]))))

adf.test(coredata(log(GoldSilver[, "silver"])))
adf.test(diff(coredata(log(GoldSilver[, "silver"]))))
kpss.test(coredata(log(GoldSilver[, "silver"])))
kpss.test(diff(coredata(log(GoldSilver[, "silver"]))))

```
Gold:
The p-value of ADF is 0.92 which is larger than 0.05, so it is nonstationary.
The p-value of KPSS is 0.01 which is smaller than 0.05, so it is nonstationary.

First order differences:
The p-value of ADF is 0.01 which is smaller than 0.05, so it is stationary.
The p-value of KPSS is 0.1 which is smaller than 0.05, so it is stationary.

Silver: 
The p-value of ADF is 0.79 which is larger than 0.05, so it is nonstationary.
The p-value of KPSS is 0.01 which is smaller than 0.05, so it is nonstationary.

First order differences:
The p-value of ADF is 0.01 which is smaller than 0.05, so it is stationary.
The p-value of KPSS is 0.1 which is smaller than 0.05, so it is stationary.


Next, let us fit the ARIMA model to gold and silver price.

```{r}
library(forecast)
gsg.arima = auto.arima(coredata(log(GoldSilver[, "gold"])), seasonal=FALSE, stepwise=FALSE, approximation=FALSE)
gss.arima = auto.arima(coredata(log(GoldSilver[, "silver"])), seasonal=FALSE, stepwise=FALSE, approximation=FALSE)

```
Both ARIMA models seem to be a good fit for the prices.


To investigate whether gold and silver prices are cointegrated, we fit a linear regression model (logGoldPrice = B0 + B1×logSilverPrice + e) and plot the residuals. 

```{r}
gs.lm = lm(coredata(log(GoldSilver[,"gold"]))~coredata(log(GoldSilver[,"silver"])))
plot(gs.lm$residuals, type="l")
```
The residual plot seems to be nonstationary.

Next, we perform the Phillips-Ouliaris Cointegration test for gold and silver prices.

```{r}
po.test(log(coredata(GoldSilver)))
```
We can see that the gold and silver prices are not cointergrated.
